### 2015-07-07 thesis/thesis/chap2/chap2.tex
changes

Furthermore, there are a number of related proposals that take
into account the correlation between (web) services and the ways
these services coordinate their actions to accomplish the required
tasks. In \cite{Jurca2007b,Jurca2005d,DBLP:conf/wise/MalikB07,Maximilien1,Yahyaoui}, the
authors propose to rank services based on their reputation in the
system and to use this ranking as a means to facilitate
cooperation of services. In those models, services rely on one
another on the basis of the reputation ranking system, using,
among other parameters, the QoS \cite{Qian-Tao-2012}. There are
other models that facilitate cooperation mechanisms among services
using various techniques. Examples of those techniques include 1)
coordination between two types of behaviors associated with
component services: operational and control behaviors
\cite{Yahyaoui3}; 2) Services-based workflows \cite{Wu-2011}; 3)
transaction-based approaches \cite{Gao,Rosario}; 4) agent
coordination mechanisms \cite{Charif,Gutierrez-Garcia-2013}; 5)
logical techniques \cite{Okutan,Tang}; and 6) community models,
which are virtual structures that aim at increasing the visibility
of services and facilitating their discovery and composition by
hosting and gathering services having similar or complementary
functionalities but different QoS parameters
\cite{Khosravifar2010}. %There are also some frameworks
%\cite{Ferguson,Ferguson2} that consider game-theoretic analysis on
%the expected payoffs obtained via different acting strategies.
However, deciding about which strategy to choose when services are
competing but still need to cooperate to accomplish complex tasks
has not been addressed and kept as open issue in all these
proposals as faithfully argued in
\cite{Maamar2011,Khosravifar-ICSOC2012}.

>>>>

Furthermore, there are a number of related proposals that take
into account the correlation between (web) services and the ways
these services coordinate their actions to accomplish the required
tasks. In \cite{Jurca2007b,Jurca2005d,DBLP:conf/wise/MalikB07,Maximilien:2001:REW:844331.844335,journals/kbs/Yahyaoui12}, the
authors propose to rank services based on their reputation in the
system and to use this ranking as a means to facilitate
cooperation of services. In those models, services rely on one
another on the basis of the reputation ranking system, using,
among other parameters, the QoS \cite{Tao:2012:NPA:2064113.2064479}. There are
other models that facilitate cooperation mechanisms among services
using various techniques. Examples of those techniques include 1)
coordination between two types of behaviors associated with
component services: operational and control behaviors
\cite{DBLP:journals/ijwgs/YahyaouiMB10}; 2) Services-based workflows \cite{Wu2011}; 3)
transaction-based approaches \cite{Gao:2011:STI:2093449.2093450,DBLP:conf/icws/RosarioBHJ07}; 4) agent
coordination mechanisms \cite{DBLP:journals/aamas/CharifS13,DBLP:journals/apin/Gutierrez-GarciaS13}; 5)
logical techniques \cite{Okutan:2010:MAA:1805335.1805430,tang:automatic}; and 6) community models,
which are virtual structures that aim at increasing the visibility
of services and facilitating their discovery and composition by
hosting and gathering services having similar or complementary
functionalities but different QoS parameters
\cite{DBLP:journals/jwsr/KhosravifarBMT10}. %There are also some frameworks
%\cite{Ferguson,Ferguson2} that consider game-theoretic analysis on
%the expected payoffs obtained via different acting strategies.
However, deciding about which strategy to choose when services are
competing but still need to cooperate to accomplish complex tasks
has not been addressed and kept as open issue in all these
proposals as faithfully argued in
\cite{1fd085d030db49d9ad024f89d13faff3,DBLP:conf/icsoc/KhosravifarAABMO12}.

### 2015-07-07 thesis/thesis/chap5/chap5.tex
changes

\Gamma & \text{if $ 0 \leq \Gamma \leq 1$;}\\
0  & \text{if $\Gamma < 0$;}\\
1 & \text{if $\Gamma > 1$.}\\
\end{cases}
\end{equation}
%
For new services with no previous reputation value, we use the
bootstrapping trust technique proposed in \cite{Yahyaoui2}. This
technique consists in giving the new services a chance and observe
their behaviors for a period of testing time. The observation
sequence is modeled as a hidden Markov model that is used to
detect the behavior of the service by comparing the observation
behavior against pre-defined trust patterns. Based on the matching
result, an initial value is assigned to the service. Using this
initial reputation value, services quickly converge to their
actual and stable values using the update function.

@@

The arrival of requests for service $w$ during the time unit $t$
(denoted here by $m_w(t)$) can be modeled as a nonhomogeneous
Poisson process \cite{Khosravifar-ICWS2010,Ruggeri2005}, which
means as a Poisson process with dynamic arrival rate
$\lambda_w(x)$ where $x$ belongs to the time unit $t$. The arrival
rate is thus a function of time and typically varies significantly
from moment to moment. In nonhomogeneous Poisson process, $m_w(t)$
is expressed as follows:

@@

\begin{equation}\label{Expectation}
E^t_w = \lambda_w(t) = \sum_{n=1}^{Max_w^t} n \ p(m_w(t) = n)
\end{equation}
%
The parameter $\lambda_w(t)$ is usually estimated from data
samples using the least squares, iterative least squares, or
maximum likelihood \cite{Massey1996}.

@@

The simulation application is written in
\textit{C\#} using \textit{Visual Studio}. We performed the implementation on a single Intel Xeon X3450 machine with 6GBs of memory. Web services were modeled as a \emph{class} and using \emph{Await} and \emph{Async} models we initiated many web services, each running as a thread.  We implemented XML based messaging system (like SOAP) with request parameters and a list of XML based responses. The request contains the flight dates, the origin and destination, type of tickets, and number of guests. The response contains different flights with different companies, prices, timing, etc. A pool of services are initialized with values taken from a real dataset that includes $2507$ real services functioning on the web.
The dataset records the QoS values of $9$ parameters including \textit{availability},
\textit{throughput}, and \textit{reliability} \cite{Almasri}.

>>>>

\Gamma & \text{if $ 0 \leq \Gamma \leq 1$;}\\
0  & \text{if $\Gamma < 0$;}\\
1 & \text{if $\Gamma > 1$.}\\
\end{cases}
\end{equation}
%
For new services with no previous reputation value, we use the
bootstrapping trust technique proposed in \cite{DBLP:conf/icwe/YahyaouiZ11}. This
technique consists in giving the new services a chance and observe
their behaviors for a period of testing time. The observation
sequence is modeled as a hidden Markov model that is used to
detect the behavior of the service by comparing the observation
behavior against pre-defined trust patterns. Based on the matching
result, an initial value is assigned to the service. Using this
initial reputation value, services quickly converge to their
actual and stable values using the update function.

@@

The arrival of requests for service $w$ during the time unit $t$
(denoted here by $m_w(t)$) can be modeled as a nonhomogeneous
Poisson process \cite{DBLP:conf/icws/KhosravifarBM10,RePEc:spr:sistpr:v:8:y:2005:i:3:p:311-329}, which
means as a Poisson process with dynamic arrival rate
$\lambda_w(x)$ where $x$ belongs to the time unit $t$. The arrival
rate is thus a function of time and typically varies significantly
from moment to moment. In nonhomogeneous Poisson process, $m_w(t)$
is expressed as follows:

@@

\begin{equation}\label{Expectation}
E^t_w = \lambda_w(t) = \sum_{n=1}^{Max_w^t} n \ p(m_w(t) = n)
\end{equation}
%
The parameter $\lambda_w(t)$ is usually estimated from data
samples using the least squares, iterative least squares, or
maximum likelihood \cite{DBLP:journals/telsys/MasseyPW96}.

@@

The simulation application is written in
\textit{C\#} using \textit{Visual Studio}. We performed the implementation on a single Intel Xeon X3450 machine with 6GBs of memory. Web services were modeled as a \emph{class} and using \emph{Await} and \emph{Async} models we initiated many web services, each running as a thread.  We implemented XML based messaging system (like SOAP) with request parameters and a list of XML based responses. The request contains the flight dates, the origin and destination, type of tickets, and number of guests. The response contains different flights with different companies, prices, timing, etc. A pool of services are initialized with values taken from a real dataset that includes $2507$ real services functioning on the web.
The dataset records the QoS values of $9$ parameters including \textit{availability},
\textit{throughput}, and \textit{reliability} \cite{DBLP:conf/www/Al-MasriM07a}.
